---
title: "Enrichment analysis for GO and KEGG Pathway"
author: "Kai Guo"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This document describes how to use the EnrichR package.
Below is a simple manual for using the package

## Introduction
You can do enrichment analysis for different type of annotation data (GO,KEGG,Reactome(may need reactome.db if you work with Human,PFAM and InterPro)             

## Quick tour
```{r}
set.seed(1234)   
library(EnrichR)   
# To check if your the current species if supported !!!
showData()   
showensemble()  
showplant()
# Make the GO and KEGG Pathway data for your analysis
# find suitable species name by using showensemble()    
hsa_go<-makeGOdat(species="human",keytype="SYMBOL")
hsa_ko<-makeKOdat(species = "human",keytype="SYMBOL")
# find suitable species name supported by reactome by using showAvailableRO()
# hsa_ro<-makeROdata(species = "Homo_sapiens") 
```         
____   

### You can make annotation data from ensemble   
* If you work with plant such as rice,you can use ensemble API make annotation data   
```{r}
# rice_go<-makeplantann(species="Oryza sativa Japonica",ann_type = "GO")   #check the species name by using showplant()
# rice_ko<-makeplantann(species="Oryza sativa Japonica",ann_type = "KEGG") 
# rice_pfam<-makeplantann(species="Oryza sativa Japonica",ann_type = "PFAM")
# rice_inter<-makeplantann(species="Oryza sativa Japonica",ann_type = "InterPro")
# rice_ro<-makePlantROdat(species = "Oryza_sativa") #check the species name by using showAvailablePlants()
## MSU version GO and KEGG infromation also supported named ricego,riceko   
## Zea may V2 GO and KEGG annotation data also supported named zm_v2_go and zm_v2_ko
# we also collect Reactome database for plant, you can just use makePlantROdat function to get RO data.   
```   
----

### Simple example for enrichment analysis

```{r,fig.height=6,fig.width=6,fig.align="center",dpi=500}
df<-data.frame(gene=sample(unique(hsa_go$SYMBOL),1000),padj=abs(rnorm(1000,0,0.01)))
rownames(df)<-df$gene
res<-GE(df,GO_FILE = hsa_go,gene.cutoff = 0.01)
head(res)
```       

```{r,fig.height=6,fig.width=6,fig.align="center"}
GE.plot(resultFis =res,top=20,pvalue.cutoff = 0.05)
resk<-KE(df,KO_FILE = hsa_ko,gene.cutoff = 0.05)
head(resk)
KE.plot(resultFis = resk,top=10,pvalue.cutoff = 0.05)
```    
You can also get network graphic for any type of enrichment analysis result and also combine different enrichment result   

```{r,fig.height=6,fig.width=6,fig.align="center",dpi=500}   
netmap(df=df,rhs=res,top=20,pvalue.cutoff = 0.05,weightcut = 0.01,visNet = T)
``` 
```{r,fig.height=6,fig.width=6,fig.align="center",dpi=500} 
netmap(df=df,rhs=res,top=20,pvalue.cutoff = 0.05,weightcut = 0.01,visNet = T,nodeselect=T)
```   
```{r,fig.height=6,fig.width=6,fig.align="center",dpi=500} 
gnet(df=df,rhs=res,top=20,pvalue.cutoff = 0.05,weightcut = 0.01)
``` 
```{r,fig.height=6,fig.width=6,fig.align="center",dpi=500} 
mnetmap(df=df,gores=res[1:30,],kores=resk,pvalue.cutoff = 0.05,top=50)
```       
Have funs!
