---
title: "Functional Enrichment Analysis and Network Construction"
author: "Kai Guo"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This document describes how to use the EnrichR package.
Below is a simple manual for using the package

## Introduction
You can do enrichment analysis for different type of annotation data (GO,KEGG,Reactome(may need reactome.db if you work with Human,PFAM and InterPro)             

## Quick tour
```{r}
set.seed(1234)   
library(EnrichR)   
# To check if your the current species if supported !!!
showData()   
showensemble()  
showplant()
# Make the GO and KEGG Pathway data for your analysis
# find suitable species name by using showensemble()    
hsa_go<-makeGOdat(species="human",keytype="SYMBOL")
hsa_ko<-makeKOdat(species = "human",keytype="SYMBOL",builtin = F)
# find suitable species name supported by reactome by using showAvailableRO()
# if you want have RO data just run
# hsa_ro<-makeROdata(species = "Homo_sapiens") 
```         
____   

### Make annotation from Ensemble   
* If you work with plant such as rice,you can use ensemble API make annotation data   
```{r}
# rice_go<-makeplantann(species="Oryza sativa Japonica",ann_type = "GO")   #check the species name by using showplant()
# rice_ko<-makeplantann(species="Oryza sativa Japonica",ann_type = "KEGG") 
# rice_pfam<-makeplantann(species="Oryza sativa Japonica",ann_type = "PFAM")
# rice_inter<-makeplantann(species="Oryza sativa Japonica",ann_type = "InterPro")
# rice_ro<-makePlantROdat(species = "Oryza_sativa") #check the species name by using showAvailablePlants()
## MSU version GO and KEGG infromation also supported named ricego,riceko   
## Zea may V2 GO and KEGG annotation data also supported named zm_v2_go and zm_v2_ko
# we also collect Reactome database for plant, you can just use makePlantROdat function to get RO data.   
```   
----

### Functional Enrichment Analysis
#### Gene ontology enrichment analysis
```{r,fig.height=6,fig.width=6,fig.align="center",,fig.cap="Gene ontology enrichment analysis results"}
df<-data.frame(gene=sample(unique(hsa_go$SYMBOL),2000),padj=abs(rnorm(2000,0,0.01)))
rownames(df)<-df$gene
res<-GE(df,GO_FILE = hsa_go,gene.cutoff = 0.01)
head(res)
## Gene ontology enrichment analysis results
GE.plot(resultFis =res,top=20,usePadj=F,pvalue.cutoff=0.05)
## You can use default paramters, the command above just to show if you want use pvalue as cut off value.
## Rich Factor: The proportion of numbers of genes in specific GO terms and numbers of all genes in the specific GO terms among the whole genomes. Color scale indicates significance level. 
``` 
#### KEGG pathway enrichment analysis
```{r,fig.height=6,fig.width=6,fig.align="center",fig.cap="KEGG pathway enrichment analysis results"}  
## KEGG pathway Enrichment analysis results
resk<-KE(df,KO_FILE = hsa_ko,gene.cutoff = 0.05,builtin = F)
head(resk)
KE.plot(resultFis = resk,top=10,pvalue.cutoff = 0.05)
## Size indicates gene numbers in specific KEGG pathway          

```   
### Network Generation with enrichment results 
You can also get network graphic for any type of enrichment analysis result and also combine different enrichment result

```{r,fig.height=6,fig.width=6,fig.align="center",fig.cap="Functional relation network"}     
netmap(df=df,rhs=res,top=20,pvalue.cutoff = 0.05,weightcut = 0.01,visNet = T,nodeselect=T)
## df could be the vector you used for enrichment analysis
```          
```{r,fig.height=6,fig.width=6,fig.align="center",fig.cap="Functional relation network"}
gnet(df=df,rhs=res,top=20,pvalue.cutoff = 0.05,weightcut = 0.01,vertex.label.cex=4)
```    
```{r,fig.height=6,fig.width=6,fig.align="center",fig.cap="Functional relation network"}
mnetmap(df=df,gores=res[1:30,],kores=resk,pvalue.cutoff = 0.05,top=50)
```       
#### Get details include the input information   
```{r}      
resgo<-getdetail(res,df);
head(resgo,6);
resko<-getdetail(resk,df);
head(resko,6)
```           
## Have funs!
